Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-28 vesicle_code/docs/permeableVes/main.tex
yny

Using scaling arguments, we showed that permeability due to osmolarity
is two orders of magnitude larger than permeability due to tension, and
six orders of magnitude larger than permeability due to bending.
Therefore, future studies will investigate semipermeable membranes
suspended in a solvent with a solute concentration. The presence of a
solute is responsible for many physiological processes including cell
migration in confined
microenvironments~\cite{StrokaJiangChenEtAl2014_Cell,
papadopoulos2008aquaporins}, dialysis~\cite{wan2006}, cell
desiccation~\cite{vogl2014effect}, and
apoptosis~\cite{marchetti1996mitochondrial}.

>>>>

%Using scaling arguments, we showed that permeability due to osmolarity
%is two orders of magnitude larger than permeability due to tension, and
%six orders of magnitude larger than permeability due to bending.
%Therefore, future studies will investigate semipermeable membranes
%suspended in a solvent with a solute concentration. The presence of a
%solute is responsible for many physiological processes including cell
%migration in confined
%microenvironments~\cite{StrokaJiangChenEtAl2014_Cell,
%papadopoulos2008aquaporins}, dialysis~\cite{wan2006}, cell
%desiccation~\cite{vogl2014effect}, and
%apoptosis~\cite{marchetti1996mitochondrial}.
